Evaluation of LOOCV predictive abilities

### 2016-09-19 reports/agronomic_data.Rmd
Do not display code chunks in report

# Explore phenotypic data
Load packages
```{r packages, message = FALSE}
if (!require("pacman")) install.packages("pacman")
pacman::p_load("data.table", "ggplot2", "ggthemes", "dplyr", "forcats", 
               "viridis", "tidyr", "gridExtra", "modelr", "caret",
               "knitr", "tibble")
```

Set knitr options
```{r knitr_options, message = FALSE}
knitr::opts_knit$set(root.dir = "~/gamazon/")
```

Load data
```{r Load_Data}
pheno <- readRDS("./data/processed/Pheno_stage2.RDS")
```

Prepare agronomic data.
```{r Prepare_agro}
genos <- readRDS("./data/processed/common_genotypes.RDS")
hybrid <- genos$Hybrid
all_pheno <- pheno %>%
  rename(Observed = EST) %>%
  as_data_frame() %>%
  filter(G %in% hybrid) %>%
  select(G, Observed, Trait) %>%
  filter(Trait != "ADL") %>%
  mutate(Trait = fct_recode(Trait, 
    "FAT" = "FETT",
    "DMY" = "GTM",
    "DMC" = "GTS",
    "PRO" = "RPR",
    "SUG" = "XZ"),
         Trait = fct_relevel(Trait, 
    c("DMY", "DMC", "ADF", "FAT", "PRO", "STA", "SUG")
    ))

@@

## Skewness
A general **rule of thumb** to consider is that skewed data whose ratio of the 
highest value to the lowest value is greater than 20 have significant skewness.
The formula for the skewness statistic is
$$
\text{skewness}  = \frac{\sum (x_i - \bar{x})^{3}}{(n - 1)v^{3/2}},
$$
where $v = \frac{\sum (x_i - \bar{x})^2}{(n - 1)}$ with $x$ is the predictor
variable, $n$ is the number of values and $\bar{x}$ is the sample mean of the 
predictor.
```{r Agro_Skewness}
all_skewness <- all_pheno %>%
  group_by(Trait) %>%
  summarize(Skewness = e1071::skewness(Observed),
            Skewness = round(Skewness, digits = 2))
reduced_skewness <- reduced_pheno %>%
  group_by(Trait) %>%
  summarize(Skewness = e1071::skewness(Observed),
            Skewness = round(Skewness, digits = 2))
full_join(x = all_skewness, y = reduced_skewness,
          by = "Trait",
          suffix = c("_All", "_Reduced")) %>%
  kable(padding = 0)
```

## Distribution
```{r Full_Agro_Distribution, message = FALSE}
ggplot(all_pheno, aes(x = Observed)) +
  geom_histogram(fill = "grey", alpha = 0.5) +
  geom_histogram(data = reduced_pheno, color = "black") +
  facet_wrap(~ Trait, scales = "free") +
  theme_bw()
```

## Correlation
```{r Full_Agro_Correlation}
par(mar = c(0, 2, 0, 0),
    mfrow = c(1, 2))
all_pheno %>%
  select(-Reduced_Data) %>%
  spread(key = Trait, value = Observed) %>%
  as.data.frame() %>%
  remove_rownames() %>%
  column_to_rownames(var = "G") %>%
  cor() %>%
  corrplot::corrplot(col = viridis(256),
                     method = "color",
                     diag = FALSE,
                     type = "lower",
                     order = "hclust",
                     tl.srt = 45,
                     addCoef.col = "black",
                     tl.col = "black",
                     title = "All hybrids",
                     mar = c(0, 1, 1, 0))
reduced_pheno %>%
  filter(Reduced_Data == "yes") %>%
  select(-Reduced_Data) %>%
  spread(key = Trait, value = Observed) %>%
  as.data.frame() %>%
  remove_rownames() %>%
  column_to_rownames(var = "G") %>%
  cor() %>%
  corrplot::corrplot(col = viridis(256),
                     method = "color",
                     diag = FALSE,
                     type = "lower",
                     order = "hclust",
                     tl.srt = 45,
                     addCoef.col = "black",
                     tl.col = "black",
                     title = "Reduced hybrids",
                     mar = c(0, 1, 1, 0))
```

>>>>

# Agronomic Data
```{r echo = FALSE, message = FALSE}
if (!require("pacman")) install.packages("pacman")
pacman::p_load("data.table", "ggplot2", "ggthemes", "dplyr", "forcats", 
               "viridis", "tidyr", "gridExtra", "modelr", "caret",
               "knitr", "tibble")

knit_hooks$set(inline = function(x) {
  prettyNum(x, big.mark = ",", digits = 2)
})
knitr::opts_knit$set(root.dir = "~/gamazon/",
                     inline = TRUE)
knitr::opts_chunk$set(fig.width = 8, fig.height = 6, echo = FALSE, 
                      warning = FALSE, echo = FALSE)
```

```{r echo = FALSE}
# Load data
pheno <- readRDS("./data/processed/Pheno_stage2.RDS")

# Prepare agronomic data.
genos <- readRDS("./data/processed/common_genotypes.RDS")
hybrid <- genos$Hybrid
all_pheno <- pheno %>%
  rename(Observed = EST) %>%
  as_data_frame() %>%
  filter(G %in% hybrid) %>%
  select(G, Observed, Trait) %>%
  filter(Trait != "ADL") %>%
  mutate(Trait = fct_recode(Trait, 
    "FAT" = "FETT",
    "DMY" = "GTM",
    "DMC" = "GTS",
    "PRO" = "RPR",
    "SUG" = "XZ"),
         Trait = fct_relevel(Trait, 
    c("DMY", "DMC", "ADF", "FAT", "PRO", "STA", "SUG")
    ))

@@

## Skewness
A general **rule of thumb** to consider is that skewed data whose ratio of the 
highest value to the lowest value is greater than 20 have significant skewness.
The formula for the skewness statistic is
$$
\text{skewness}  = \frac{\sum (x_i - \bar{x})^{3}}{(n - 1)v^{3/2}},
$$
where $v = \frac{\sum (x_i - \bar{x})^2}{(n - 1)}$ with $x$ is the predictor
variable, $n$ is the number of values and $\bar{x}$ is the sample mean of the 
predictor.
```{r Agro-Skewness, echo = FALSE}
all_skewness <- all_pheno %>%
  group_by(Trait) %>%
  summarize(Skewness = e1071::skewness(Observed),
            Skewness = round(Skewness, digits = 2))
reduced_skewness <- reduced_pheno %>%
  group_by(Trait) %>%
  summarize(Skewness = e1071::skewness(Observed),
            Skewness = round(Skewness, digits = 2))
full_join(x = all_skewness, y = reduced_skewness,
          by = "Trait",
          suffix = c(" (Full)", " (Reduced)")) %>%
  kable(padding = 0)
```

## Distribution
```{r Agro-Distribution, message = FALSE, echo = FALSE, fig.cap = "Histogram of the distribution of seven agronomic traits. Black bins show the distribution of the reduced set of hybrids whereas light grey bins show the distribtution of the full set of hybrids."}
ggplot(all_pheno, aes(x = Observed)) +
  geom_histogram(fill = "grey", alpha = 0.5) +
  geom_histogram(data = reduced_pheno, color = "black") +
  facet_wrap(~ Trait, scales = "free") +
  theme_bw()
```

## Correlation
```{r Agro-Correlation, echo = FALSE, fig.cap = "Pairwise correlations among seven agronomic traits for the full set of hybrids and the reduced set of hybrids, respectively."}
par(mar = c(0, 1, 0, 0),
    mfrow = c(1, 2))
all_pheno %>%
  select(-Reduced_Data) %>%
  spread(key = Trait, value = Observed) %>%
  as.data.frame() %>%
  remove_rownames() %>%
  column_to_rownames(var = "G") %>%
  cor() %>%
  corrplot::corrplot(col = viridis(256),
                     method = "color",
                     diag = FALSE,
                     cl.pos = "b",
                     tl.pos = "d",
                     tl.srt = 60,
                     order = "hclust",
                     addCoef.col = "black",
                     title = "Full",
                     mar = c(0, 1, 1, 0))
reduced_pheno %>%
  filter(Reduced_Data == "yes") %>%
  select(-Reduced_Data) %>%
  spread(key = Trait, value = Observed) %>%
  as.data.frame() %>%
  remove_rownames() %>%
  column_to_rownames(var = "G") %>%
  cor() %>%
  corrplot::corrplot(col = viridis(256),
                     method = "color",
                     diag = FALSE,
                     cl.pos = "b",
                     tl.pos = "d",
                     tl.srt = 60,
                     order = "hclust",
                     addCoef.col = "black",
                     title = "Reduced",
                     mar = c(0, 1, 1, 0))
```

### 2016-09-19 reports/index.Rmd
Do not display code chunks in report

@@

>>>>

Here, we are working with a "full" or "complete" data set &mdash; referring to 
the maximum number of hybrids for which agronomic and genomic, but not 
necessarily transcriptomic data are available &mdash; and a "reduced" data set
with less hybrids but all of their parental inbred lines having complete
genomic and transcriptomic records.

All our predictive abilities were evaluated using a leave-one-out cross 
validation (LOOCV) routine.

@@

## Overview
Chapter \@ref(introduction) gives a summary of the relevant literature.

Chapter \@ref(data-overview) provides a brief summary of the available data 
without delving into their properties.

Chapter \@ref(agronomic-data) gives an overview of the distribution of the 
agronomic traits as well as correlations among them, separately for the full
set of hybrids as well as the reduced set of hybrids.

Chapter \@ref(prediction-for-reduced-data) deals with the results of hybrid 
prediction for the reduced set of data.

Chapter \@ref(evaluation-of-loocv-predictive-abilities) examines the influence
of certain levels of missingness in the transcriptomic data.

### 2016-09-19 reports/na_fraction_pheno_predability.Rmd
Move report on Pred_Ability with NAs in parents
Bundle reports in one gitbook
Do not display code chunks in report

---
title: "Evaluation of LOOCV predictive abilities"
output: 
  html_document:
    toc: true
    toc_float: true
    smooth_scroll: true
    toc_depth: 3
    number_sections: true
    theme: lumen
    highlight: tango
    fig_width: 8
    fig_height: 5
---

# Data preparation
Load packages
```{r message = FALSE}
if (!require("pacman")) install.packages("pacman")
pacman::p_load("data.table", "ggplot2", "ggthemes", "dplyr", "forcats", 
               "viridis", "tidyr", "gridExtra", "modelr", "MASS")
```

Set knitr options
```{r message = FALSE}
knitr::opts_knit$set(root.dir = "~/gamazon/")
```

Load log files and data
```{r Load_Data, cache = TRUE}
run_log <- fread("./data/derived/pred_log.txt")

# LOOCV 
loocv_nms <- run_log[CV == "LOOCV", Job_ID, ]
loocv <- lapply(seq_along(loocv_nms), FUN = function(i) {
  readRDS(paste0("./data/derived/predictions/", loocv_nms[i], ".RDS"))
})
loocv <- rbindlist(loocv)
```

Change trait names and compute residuals.
```{r Rename_Traits, cache = TRUE}
loocv_clean <- loocv %>%
  mutate(Trait = fct_recode(Trait, 
                            "FAT" = "FETT",
                            "PRO" = "RPR",
                            "DMY" = "GTM",
                            "DMC" = "GTS"),
         Trait = fct_relevel(Trait, c("DMY", "DMC", "ADF", "FAT", "PRO", "STA",
                                      "XZ")),

         Dent_NA_Fraction = as.factor(as.character(Dent_NA_Fraction)),
         Flint_NA_Fraction = as.factor(as.character(Flint_NA_Fraction)),
         Residuals = y - yhat
  )
```

## Predictive ability for non-imputed data
Peak at predictive abilities based on non-imputed predictor information and rank
the results by their predictive ability.
```{r Non_Imputed_Pred_Ability, cache = TRUE}
loocv_clean %>%
  filter(Dent_NA_Fraction == 0, Flint_NA_Fraction == 0) %>%
  mutate(Predictor = as.factor(Predictor)) %>%
  droplevels() %>%
  group_by(Predictor, Trait) %>%
  summarize(Pred_Ability = cor(y, yhat)) %>%
  arrange(desc(Pred_Ability))
```

# Plots
## Complete data (no ssBLUP)
### Predicted vs. residuals
```{r Complete_Data_Residuals, cache = TRUE}
full_pred_resid <- loocv_clean %>%
  filter(Dent_NA_Fraction == 0, Flint_NA_Fraction == 0) %>%
  group_by(Predictor) %>%
  do(plot = ggplot(., aes(x = yhat, y = Residuals)) +
       geom_point(size = 0.5) +
       geom_ref_line(h = 0) +
       facet_wrap(~ Trait, nrow = 2, scales = "free") +
       theme(axis.text.x = element_text(angle = 60, hjust = 1, vjust = 1)) +
       xlab("Predicted") +
       ylab("Residuals") +
       ggtitle(.$Predictor))
invisible(lapply(full_pred_resid$plot, FUN = print))
```

### Predicted vs. Observed
```{r Complete_Data_y_yHat, cache = TRUE}
full_y_yhat <- loocv_clean %>%
  filter(Dent_NA_Fraction == 0, Flint_NA_Fraction == 0) %>%
  group_by(Predictor) %>%
  do(plot = ggplot(., aes(x = y, y = yhat)) +
       geom_point(size = 0.5) +
       geom_abline(slope = 1, linetype = "dashed", color = "blue") +
       facet_wrap(~ Trait, nrow = 2, scales = "free") +
       theme(axis.text.x = element_text(angle = 60, hjust = 1, vjust = 1)) +
       xlab("Predicted") +
       ylab("Residuals") +
       ggtitle(.$Predictor))
invisible(lapply(full_y_yhat$plot, FUN = print))
```

## Imputed data
### Predicted vs. residuals
Generate residual plots for each trait and each combination of missing values 
in Dent (rows) and Flint (columns) parents.
```{r Imputed_Residual, cache = TRUE}
resid_plots <- loocv_clean %>%
  filter(Predictor == "mrna") %>%
  group_by(Trait) %>%
  do(plot = ggplot(., aes(x = yhat, y = Residuals)) +
            geom_point(size = 0.5) +
            geom_ref_line(h = 0) +
            facet_grid(Dent_NA_Fraction ~ Flint_NA_Fraction) +
            theme_light() +
            theme(axis.text.x = element_text(angle = 60, 
                                             hjust = 1, vjust = 1)) +
            xlab("Predicted") +
            ylab("Residuals") +
            ggtitle(.$Trait))
invisible(lapply(resid_plots$plot, print))
```

### Predicted vs. observed
Likewise, compare observed with predicted values for combinations that were used
in the previous plot.
```{r Imputed_y_yHat, cache = TRUE}
y_yhat_plots <- loocv_clean %>%
  filter(Predictor == "mrna") %>%
  group_by(Trait) %>%
  do(plot = ggplot(., aes(x = y, y = yhat)) +
            geom_point(size = 0.5) +
            geom_abline(slope = 1, linetype = "dashed", color = "blue") +
            facet_grid(Dent_NA_Fraction ~ Flint_NA_Fraction) +
            theme(axis.text.x = element_text(angle = 60,
                                             hjust = 1, vjust = 1)) +
            xlab("Observed") +
            ylab("Predicted") +
            ggtitle(.$Trait))
invisible(lapply(y_yhat_plots$plot, print))
```

## LOOCV predictive ability (DMY)
### mrna
```{r DMY, cache = TRUE}
dmy <- loocv_clean %>%
  mutate(Dent_NA_Fraction = as.numeric(as.character(Dent_NA_Fraction)),
         Flint_NA_Fraction = as.numeric(as.character(Flint_NA_Fraction))) %>%
  filter(Trait == "DMY", Predictor == "mrna") %>%
  droplevels() %>%
  unite(NA_Fraction, Dent_NA_Fraction, Flint_NA_Fraction, sep = "_") %>%
  group_by(Predictor, Trait, NA_Fraction) %>%
  summarize(Pred_Ability = cor(y, yhat)) %>%
  ungroup() %>%
  arrange(desc(Pred_Ability)) %>%
  separate(NA_Fraction,
           into = c("Dent_NA_Fraction", "Flint_NA_Fraction"), 
           sep = "_") %>%
  mutate(Dent_NA_Fraction = as.numeric(Dent_NA_Fraction),
         Flint_NA_Fraction = as.numeric(Flint_NA_Fraction)) %>%
  rowwise() %>%
  mutate(Avg_NA = mean(c(Dent_NA_Fraction, Flint_NA_Fraction)))
```

### Average r as a function of global missingness and missingness in Flint
```{r DMY_Global_NA_Flint_NA, cache = TRUE}
dmy %>%
  mutate(Flint_NA_Fraction = as.factor(as.character(Flint_NA_Fraction))) %>%
  mutate(Flint_NA_Fraction = fct_relevel(Flint_NA_Fraction, 
                                         "0", "0.1", "0.2", "0.3", "0.4",
                                         "0.5", "0.6")) %>%
  arrange(desc(Avg_NA)) %>%
  ggplot(aes(x = Avg_NA, y = Pred_Ability, color = Flint_NA_Fraction)) +
  geom_point(size = 2) +
  geom_line() +
  geom_smooth(method = "rlm", aes(group = 1)) +
  theme_light() +
  ylab("r")
```

### Average r as a function of missingness in Dent and missingness in Flint
```{r DMY_Dent_NA_Flint_NA, cache = TRUE}
dmy %>%
  mutate(Flint_NA_Fraction = as.factor(as.character(Flint_NA_Fraction))) %>%
  mutate(Flint_NA_Fraction = fct_relevel(Flint_NA_Fraction, 
                                         "0", "0.1", "0.2", "0.3", "0.4",
                                         "0.5", "0.6")) %>%
  arrange(desc(Dent_NA_Fraction)) %>%
  ggplot(aes(x = Dent_NA_Fraction, y = Pred_Ability, 
             color = Flint_NA_Fraction)) +
  geom_point(size = 2) +
  geom_line() +
  geom_smooth(method = "rlm", aes(group = 1)) +
  theme_light() +
  ylab("r")
```

### Predictive ability as a function of missingness in Dent and missingness in 
### Flint for all traits
```{r All_Traits_Dent_NA_Flint_NA, cache = TRUE} 
loocv_clean %>%
  filter(Dent_NA_Fraction != 0, Flint_NA_Fraction != 0) %>%
  unite(NA_Fraction, Dent_NA_Fraction, Flint_NA_Fraction, sep = "_") %>%
  group_by(Trait, NA_Fraction) %>%
  summarize(Pred_Ability = cor(y, yhat)) %>%
  ungroup() %>%
  separate(NA_Fraction, into = c("Dent_NA_Fraction",
                                 "Flint_NA_Fraction"), sep = "_") %>%
  mutate(Dent_NA_Fraction = as.numeric(Dent_NA_Fraction)) %>%
  ggplot(aes(x = Dent_NA_Fraction, y = Pred_Ability, 
             color = Flint_NA_Fraction)) +
  geom_line() +
  facet_wrap(~ Trait, scales = "free_x") +
  theme_light() +
  scale_color_viridis(discrete = TRUE) +
  theme(legend.position = "top") +
  ylab("r")
```

>>>>

# Evaluation of LOOCV predictive abilities
```{r message = FALSE}
if (!require("pacman")) install.packages("pacman")
pacman::p_load("data.table", "ggplot2", "ggthemes", "dplyr", "forcats", 
               "viridis", "tidyr", "gridExtra", "modelr", "MASS")
knit_hooks$set(inline = function(x) {
  prettyNum(x, big.mark = ",", digits = 2)
})
knitr::opts_knit$set(root.dir = "~/gamazon/",
                     inline = TRUE)
knitr::opts_chunk$set(fig.width = 8, fig.height = 6, echo = FALSE, 
                      warning = FALSE, echo = FALSE)
```

### Predicted vs. residuals
Generate residual plots for each trait and each combination of missing values 
in Dent (rows) and Flint (columns) parents.
```{r Imputed-Residual, cache = TRUE, dependson = "Rename-Traits"}
resid_plots <- loocv_clean %>%
  filter(Predictor == "mRNA") %>%
  group_by(Trait) %>%
  do(plot = ggplot(., aes(x = yhat, y = Residuals)) +
            geom_point(size = 0.5) +
            geom_ref_line(h = 0) +
            facet_grid(Dent_NA_Fraction ~ Flint_NA_Fraction) +
            theme_light() +
            theme(axis.text.x = element_text(angle = 60, 
                                             hjust = 1, vjust = 1)) +
            xlab("Predicted") +
            ylab("Residuals") +
            ggtitle(.$Trait))
invisible(lapply(resid_plots$plot, print))
```

### Predicted vs. observed
Likewise, compare observed with predicted values for combinations that were used
in the previous plot.
```{r Imputed-y-yHat, cache = TRUE, dependson = "Rename-Traits"}
y_yhat_plots <- loocv_clean %>%
  filter(Predictor == "mRNA") %>%
  group_by(Trait) %>%
  do(plot = ggplot(., aes(x = y, y = yhat)) +
            geom_point(size = 0.5) +
            geom_abline(slope = 1, linetype = "dashed", color = "blue") +
            facet_grid(Dent_NA_Fraction ~ Flint_NA_Fraction) +
            theme(axis.text.x = element_text(angle = 60,
                                             hjust = 1, vjust = 1)) +
            xlab("Observed") +
            ylab("Predicted") +
            ggtitle(.$Trait))
invisible(lapply(y_yhat_plots$plot, print))
```

## LOOCV predictive ability (DMY)
### mrna
```{r DMY, cache = TRUE, dependson = "Rename-Traits"}
dmy <- loocv_clean %>%
  mutate(Dent_NA_Fraction = as.numeric(as.character(Dent_NA_Fraction)),
         Flint_NA_Fraction = as.numeric(as.character(Flint_NA_Fraction))) %>%
  filter(Trait == "DMY", Predictor == "mRNA") %>%
  droplevels() %>%
  unite(NA_Fraction, Dent_NA_Fraction, Flint_NA_Fraction, sep = "_") %>%
  group_by(Predictor, Trait, NA_Fraction) %>%
  summarize(Pred_Ability = cor(y, yhat)) %>%
  ungroup() %>%
  arrange(desc(Pred_Ability)) %>%
  separate(NA_Fraction,
           into = c("Dent_NA_Fraction", "Flint_NA_Fraction"), 
           sep = "_") %>%
  mutate(Dent_NA_Fraction = as.numeric(Dent_NA_Fraction),
         Flint_NA_Fraction = as.numeric(Flint_NA_Fraction)) %>%
  rowwise() %>%
  mutate(Avg_NA = mean(c(Dent_NA_Fraction, Flint_NA_Fraction)))
```

### Average r as a function of global missingness and missingness in Flint
```{r DMY_Global_NA_Flint_NA, cache = TRUE, dependson = "DMY"}
dmy %>%
  mutate(Flint_NA_Fraction = as.factor(as.character(Flint_NA_Fraction))) %>%
  mutate(Flint_NA_Fraction = fct_relevel(Flint_NA_Fraction, 
                                         "0", "0.1", "0.2", "0.3", "0.4",
                                         "0.5", "0.6")) %>%
  arrange(desc(Avg_NA)) %>%
  ggplot(aes(x = Avg_NA, y = Pred_Ability, color = Flint_NA_Fraction)) +
  geom_point(size = 2) +
  geom_line() +
  geom_smooth(method = "rlm", aes(group = 1)) +
  theme_light() +
  ylab("r")
```

### Average r as a function of missingness in Dent and missingness in Flint
```{r DMY_Dent_NA_Flint_NA, cache = TRUE, dependson = "DMY"}
dmy %>%
  mutate(Flint_NA_Fraction = as.factor(as.character(Flint_NA_Fraction))) %>%
  mutate(Flint_NA_Fraction = fct_relevel(Flint_NA_Fraction, 
                                         "0", "0.1", "0.2", "0.3", "0.4",
                                         "0.5", "0.6")) %>%
  arrange(desc(Dent_NA_Fraction)) %>%
  ggplot(aes(x = Dent_NA_Fraction, y = Pred_Ability, 
             color = Flint_NA_Fraction)) +
  geom_point(size = 2) +
  geom_line() +
  geom_smooth(method = "rlm", aes(group = 1)) +
  theme_light() +
  ylab("r")
```

### Predictive ability as a function of missingness in Dent and missingness in 
### Flint for all traits
```{r All_Traits_Dent_NA_Flint_NA, cache = TRUE, dependson = "Rename-Trait"} 
loocv_clean %>%
  filter(Dent_NA_Fraction != 0, Flint_NA_Fraction != 0) %>%
  unite(NA_Fraction, Dent_NA_Fraction, Flint_NA_Fraction, sep = "_") %>%
  group_by(Trait, NA_Fraction) %>%
  summarize(Pred_Ability = cor(y, yhat)) %>%
  ungroup() %>%
  separate(NA_Fraction, into = c("Dent_NA_Fraction",
                                 "Flint_NA_Fraction"), sep = "_") %>%
  mutate(Dent_NA_Fraction = as.numeric(Dent_NA_Fraction)) %>%
  ggplot(aes(x = Dent_NA_Fraction, y = Pred_Ability, 
             color = Flint_NA_Fraction)) +
  geom_line() +
  facet_wrap(~ Trait, scales = "free_x") +
  theme_light() +
  scale_color_viridis(discrete = TRUE) +
  theme(legend.position = "top") +
  ylab("r")
```
